---
title: "Scholarship Administration Survey"
author: "Larry Liu"
date: "May 24, 2016"
output: html_document
---

First, we load in all of the data and clean the data (i.e. remove subjects who failed the attention check).
```{r}
#Read in the data
data = read.csv("C:/Users/Larry/Dropbox/Stanford University/2015-2016/Spring Quarter/PSYCH 154/replicationData.csv")

n_collected = nrow(data)
print(n_collected)
```

A total of 301 subjects completed our Qualtrics survey. However, not all of them passed the attention check.

```{r}
#Filter out all results that fail the attention check
data = data[data$Q11==3,]

#Number of valid entries
n = nrow(data)
n
```
There were 267 total subjects that passed the attention check, while 34 failed. We perform analysis only on the 267 subjects that passed.

Next, we want to tabulate the results in order to perform a chi-squared test for Prize Package 1.
```{r}
PP1vector = c(nrow(data[data$Q1==1,]),nrow(data[data$Q2==1,]),nrow(data[data$Q1==2,]),nrow(data[data$Q2==2,]))
PP1matrix = matrix(PP1vector,nrow=2,ncol=2)
PP1 = data.frame(PP1matrix)
colnames(PP1) = c("Choice A", "Choice B")
rownames(PP1) = c("Q1", "Q2")

PP1 #Absolute joint distribution
PP1/n #Probabilistic joint distribution
chisq.test(PP1)
```

Next, we want to tabulate the results in order to perform a chi-squared test for Prize Package 2.
```{r}
PP2vector = c(nrow(data[data$Q4==1,]),nrow(data[data$Q5==1,]),nrow(data[data$Q4==2,]),nrow(data[data$Q5==2,]))
PP2matrix = matrix(PP2vector,nrow=2,ncol=2)
PP2 = data.frame(PP2matrix)
colnames(PP2) = c("Choice A", "Choice B")
rownames(PP2) = c("Q4", "Q5")

PP2 #Absolute joint distribution
PP2/n #Probabilistic joint distribution
chisq.test(PP2)
```

For the Allais Paradox to be supported, more subjects had to choose option "B" in Question 2  (the inequality-averse choice), than in Question 1. The results showed that subjects indeed chose the inequality-averse option to a significant degree, therefore, the Allais Paradox is supported.
 
For the inequality peanuts effect to be supported, more subjects had to choose the inequality averse option (B) in Question 5 (the control) than in Question 4, where the stakes were too small.  This is supported by our data, indicating the inequality peanuts affect at work. 